Autocorrelation in Sparse Distributed Memory

### 2018-11-09 Chapters/sdm-autocorrelation.tex
Intro; outline; etc.
IEEE paper
minor
Alignment respecting column borders

@@

    \begin{align}
    \frac{n-k}{n} \binom{n}{k} = \frac{(n-k)}{n} \frac{n!}{(n-k)! k!} = \frac{(n-1)!}{k! (n-1-k)!} = \binom{n-1}{k}
    \end{align}

@@

\begin{align}
P(\text{cnt}_i \ge 0 | \text{addr}_i = 1) = P(\text{cnt}_i \le 0 | \text{addr}_i = 0) = 1 - \mathcal{N}.\text{cdf}(0)
\end{align}

@@

\begin{align}
\sum_{k=1}^{Z} \left[ \text{cnt}_k | \text{addr}_k=\eta_1 \right] &\sim \mathcal{N}(\mu = \mu_\text{cnt} \mu_Z, \sigma^2 = \sigma_\text{cnt}^2 \mu_Z + \mu_\text{cnt}^2 \sigma^2_Z) \label{eqn:sdm-eta1-addr1} \\
\sum_{k=1}^{h-Z} \left[ \text{cnt}_k | \text{addr}_k \ne \eta_1 \right] &\sim \mathcal{N}(\mu = -\mu_\text{cnt} (1-p) \mu_h, \sigma^2 = \sigma^2_\text{cnt} (1-p) \mu_h + \mu_\text{cnt}^2 \sigma^2_{h-Z}) \label{eqn:sdm-eta1-addr0}
\end{align}

@@

\begin{align}
P(wrong) &= P(\text{acc}_i < 0 | \eta_i = 1) \cdot P(\eta_i = 1) + P(\text{acc}_i > 0 | \eta_i = 0) \cdot P(\eta_i = 0) \\
    &= \frac{\mathcal{N}_{\eta_i=1}.\text{cdf}(0)}{2} + \frac{1-\mathcal{N}_{\eta_i=0}.\text{cdf}(0)}{2} \\
    &= \frac{\mathcal{N}_{\eta_i=1}.\text{cdf}(0)}{2} + \frac{\mathcal{N}_{\eta_i=1}.\text{cdf}(0)}{2} \\
    &= \mathcal{N}_{\eta_i=1}.\text{cdf}(0)
\end{align}

>>>>

\citet{Kanerva1994}

@@

    \begin{align}
    \frac{n-k}{n} \binom{n}{k} = \binom{n-1}{k}
    \end{align}

@@

\begin{align}
P(\text{cnt}_i \ge 0 | \text{addr}_i = 1) = P(\text{cnt}_i \le 0 | \text{addr}_i = 0) \\
 = 1 - \mathcal{N}.\text{cdf}(0)
\end{align}

@@

\begin{align}
\begin{split}
\sum_{k=1}^{Z} \left[ \text{cnt}_k | \text{addr}_k=\eta_1 \right] &\sim \\
& \mathcal{N}(\mu = \mu_\text{cnt} \mu_Z, \sigma^2 = \sigma_\text{cnt}^2 \mu_Z + \mu_\text{cnt}^2 \sigma^2_Z) \label{eqn:sdm-eta1-addr1}
\end{split}
\end{align}
, and, respectively:

\begin{align}
\begin{split}
& \sum_{k=1}^{h-Z} \left[ \text{cnt}_k | \text{addr}_k \ne \eta_1 \right] \sim \\
& \mathcal{N}(\mu = -\mu_\text{cnt} (1-p) \mu_h, \sigma^2 = \sigma^2_\text{cnt} (1-p) \mu_h + \mu_\text{cnt}^2 \sigma^2_{h-Z}) \label{eqn:sdm-eta1-addr0}
\end{split}
\end{align}

@@

\begin{align*}
P(wrong) = P(\text{acc}_i < 0 | \eta_i = 1) \cdot P(\eta_i = 1) {}& \\
+P(\text{acc}_i > 0 | \eta_i = 0) \cdot P(\eta_i = 0) \\
= \frac{\mathcal{N}_{\eta_i=1}.\text{cdf}(0)}{2} + \frac{1-\mathcal{N}_{\eta_i=0}.\text{cdf}(0)}{2} \\
= \frac{\mathcal{N}_{\eta_i=1}.\text{cdf}(0)}{2} + \frac{\mathcal{N}_{\eta_i=1}.\text{cdf}(0)}{2} \\
= \mathcal{N}_{\eta_i=1}.\text{cdf}(0)
\end{align*}
